%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Amanda Tran - Resume
% 10/20/2017
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}
\usepackage{wasysym}
\usepackage[utf8]{inputenc}
\usepackage[hmargin=1.0cm, vmargin=1.0cm]{geometry}
\linespread{0.95}
%\usepackage[margin=2in]{geometry}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Amanda Tran}
{\urlstyle{same}
	\phone \hspace{0.1mm} {(206) 579-0876}\\
	\faEnvelope \hspace{0.1mm} {amanda.tran02@gmail.com}\\
	\faLinkedinSquare \hspace{0.1mm} {www.linkedin.com/in/amandatran02}
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.22\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\subsection{University of \\Washington}
\descript{B.S. Electrical Engineering}
%Concentration: Power Electronics
Major GPA: 3.64\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
Python, Bash, MATLAB, Fusion360, Blender, KiCAD, C++, Precision Soldering, Logic Analyzers, Oscilloscopes, 3D Printers, Test Automation, Technical Writing, Project Management, Requirements Tracking 
% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
• Controls Systems Analysis \\
• Matrix Algebra with Applications\\
• Computer Programming II\\
• Scientific Computing\\
• Engineering Statistics\\
• Advance Multivariable Calculus\\
• Design of Digital Circuits \\
• Discrete Signals and Systems\\
• Embedded Systems\\
%Power System Analysis \\
%Power Electronic Design \\
%Energy Systems \\
%Wind Energy \\
%Engineering Statics\\
\sectionsep


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
• UW Dean's List\\
• William and Margaret Paynter Endowed Scholarship\\
• WA RUC Smartphone Innovation Challenge Winner\\
• 2-time Rhythmic Gymnastics USA National Team Member\\
\sectionsep

%\sectionsep
%\DTMsetdatestyle{mylastupdate}
%\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.76\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\workplace{BluOasis Corporation }{June 2021–July 2022} \\
\position{Product Lead}{Seattle, WA}
\vspace{0.6em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  Hardware Stuff - 5V supply design, test, and deployment. Design implemented dual redundancy, isolated orring output. designed current sense board for solar panels. 
\item FW/SW Stuff - managed ICD for communication across all subsystems. debugged communication and increased communication reliability. 
\item Project Management stuff - overseeing contractors, SOW, requirement tracking and test campaign 
\item marketing stuff
\item client and vendor relations
\end{tightemize}
\sectionsep

\workplace{LeoStella LLC}{May 2019-June 2021} \\
\position{Assembly, Integration, Test Automation Engineer}{Tukwila, WA}
\begin{tightemize}
%\item Researched the technology to develop an implantable oral sensor as a medical monitoring device. 
\item Lead Assembly, Integration, and Test team, overseeing AIT planning and execution for Loft Orbital customer contract. 
\item Automated and maintained code base for component-, subsystem-, and system-level tests reducing takt time and operator error. 
\item Oversaw functional, environmental, and performance testing of all components, subsystems, and the completed satellites.
\item Performed anomaly and failure tracking and resolution
\item Oversaw launch-site test and launch vehicle integration onto SpaceX Falcon 9 fairing.
\item Lead Rocket Lab launch campaign at launch site in Mahia, New Zealand 
\end{tightemize}
\sectionsep 

\workplace{Microsoft}{Mar 2018-May 2019} \\
\position{Hardware Test Engineer }{Redmond, WA}
\begin{tightemize}
%\item Researched the technology to develop an implantable oral sensor as a medical monitoring device. 
\item Verifying and validating Microsoft Surface displays to ensure product meets power and high speed signal specifications.
\item Automated loading stress tests using PowerShell and Python.
\end{tightemize}
\sectionsep 

\workplace{Astronics Advance Electronic Systems}{Jun 2017–Sept 2017} \\
\position{Electrical Engineering Intern }{Kirkland, WA}
%\vspace{0.6em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Investigated failed Seat Power units by debugging PCB, preforming root failure analysis, writing technical reports on failure mode and proposed fix.
%\item Developed OMM and V\&V procedures, increasing reliability of Qual testing
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extra Curricular 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extra Curricular}
\runsubsection{Student Research Assistant}
\location{University of Washington GEMSEC Lab}
Assisted on conducting experiments to develop an enzymatic bioreactor flow cell, which has applications in sustainable energy. Operating and modifying 3D printers to print biological substances. Authorship on Peptide-Enabled Aqueous Tooth Whitening Infection-Free Implants scientific poster. Lead Presenter at Undergraduate Research Symposium.
\sectionsep

\runsubsection{Career and Technical Education Advisor}
\location{Tukwila School District}
Technical advisor on the CTE Committee to give industry advice on courses that should be added to K-12 curriculum to better prepare students for a career in STEM. Program geared towards under privileged students to close the growing opportunity gap. Industry speaker in high school career development classes. 
\sectionsep 
\end{minipage} 
\end{document}  